---
title: "Visualizations of Network Statistics Over Time Using Vertex Bootstrap and Jackknife"
author: "Alan Sun"
date: "7/15/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
source("vert-jack-viz.R")
```

This document contains visualizations showing distributions of the differences in several network statistics over time. The distributions are obtained using the vertex bootstrap and jackknife procedures. Two different temporal networks are examined.

Source code (to generate distributions): [https://github.com/alansun25/network-analysis/blob/main/analysis/vert-jack-viz.R](https://github.com/alansun25/network-analysis/blob/main/analysis/vert-jack-viz.R)

# Friendship in a Dutch school class
Data source:

- **[RSiena](https://www.stats.ox.ac.uk/~snijders/siena/)**
- Andrea Knecht
- [https://www.stats.ox.ac.uk/~snijders/siena/tutorial2010_data.htm](https://www.stats.ox.ac.uk/~snijders/siena/tutorial2010_data.htm)
- 2008\

## Original Friendship Networks
```{r echo=FALSE}
plot(fg1, layout=layout_in_circle(fg1), main = "Friendships at time 1", vertex.label.cex=0.7)
```
Transitivity: `r transitivity(fg1)`, Mean Degree: `r mean(degree(fg1))`, Edge Density: `r edge_density(fg1)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg1) > 1)`\

```{r echo=FALSE}
plot(fg2, layout=layout_in_circle(fg2), main = "Friendships at time 2 (Three months after time 1)", vertex.label.cex=0.7)
```
Transitivity: `r transitivity(fg2)`, Mean Degree: `r mean(degree(fg2))`, Edge Density: `r edge_density(fg2)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg2) > 1)`\

```{r echo=FALSE}
plot(fg3, layout=layout_in_circle(fg3), main = "Friendships at time 3 (Three months after time 2)", vertex.label.cex=0.7)
```
Transitivity: `r transitivity(fg3)`, Mean Degree: `r mean(degree(fg3))`, Edge Density: `r edge_density(fg3)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg3) > 1)`\

```{r echo=FALSE}
plot(fg4, layout=layout_in_circle(fg4), main = "Friendships at time 4 (Three months after time 3)", vertex.label.cex=0.7)
```
Transitivity: `r transitivity(fg4)`, Mean Degree: `r mean(degree(fg4))`, Edge Density: `r edge_density(fg4)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg4) > 1)`\

## Vertex Bootstrapped Distributions of Network Statistics
Transitivity:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(tboot_f1, main = "Time 1",
    xlab = "Transitivity", col = "turquoise")
hist(tboot_f2, main = "Time 2",
    xlab = "Transitivity", col = "lavender")
hist(tboot_f3, main = "Time 3",
    xlab = "Transitivity", col = "lightblue")
hist(tboot_f4, main = "Time 4",
    xlab = "Transitivity", col = "gold")
```

Mean Degree:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(mdboot_f1, main = "Time 1",
    xlab = "Mean Degree", col = "turquoise")
hist(mdboot_f2, main = "Time 2",
    xlab = "Mean Degree", col = "lavender")
hist(mdboot_f3, main = "Time 3",
    xlab = "Mean Degree", col = "lightblue")
hist(mdboot_f4, main = "Time 4",
    xlab = "Mean Degree", col = "gold")
```
Edge Density:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(dboot_f1, main = "Time 1",
    xlab = "Density", col = "turquoise")
hist(dboot_f2, main = "Time 2",
    xlab = "Density", col = "lavender")
hist(dboot_f3, main = "Time 3",
    xlab = "Density", col = "lightblue")
hist(dboot_f4, main = "Time 4",
    xlab = "Density", col = "gold")
```
Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(kboot_f1, main = "Time 1",
    xlab = "Quantity", col = "turquoise")
hist(kboot_f2, main = "Time 2",
    xlab = "Quantity", col = "lavender")
hist(kboot_f3, main = "Time 3",
    xlab = "Quantity", col = "lightblue")
hist(kboot_f4, main = "Time 4",
    xlab = "Quantity", col = "gold")
```

## Vertex Jackknife Distributions of Network Statistics
Transitivity:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(tjack_f1, main = "Time 1",
    xlab = "Transitivity", col = "turquoise")
hist(tjack_f2, main = "Time 2",
    xlab = "Transitivity", col = "lavender")
hist(tjack_f3, main = "Time 3",
    xlab = "Transitivity", col = "lightblue")
hist(tjack_f4, main = "Time 4",
    xlab = "Transitivity", col = "gold")
```

Mean Degree:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(mdjack_f1, main = "Time 1",
    xlab = "Mean Degree", col = "turquoise")
hist(mdjack_f2, main = "Time 2",
    xlab = "Mean Degree", col = "lavender")
hist(mdjack_f3, main = "Time 3",
    xlab = "Mean Degree", col = "lightblue")
hist(mdjack_f4, main = "Time 4",
    xlab = "Mean Degree", col = "gold")
```
Edge Density:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(djack_f1, main = "Time 1",
    xlab = "Density", col = "turquoise")
hist(djack_f2, main = "Time 2",
    xlab = "Density", col = "lavender")
hist(djack_f3, main = "Time 3",
    xlab = "Density", col = "lightblue")
hist(djack_f4, main = "Time 4",
    xlab = "Density", col = "gold")
```
Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(kjack_f1, main = "Time 1",
    xlab = "Quantity", col = "turquoise")
hist(kjack_f2, main = "Time 2",
    xlab = "Quantity", col = "lavender")
hist(kjack_f3, main = "Time 3",
    xlab = "Quantity", col = "lightblue")
hist(kjack_f4, main = "Time 4",
    xlab = "Quantity", col = "gold")
```

## Bootstrap distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

Transitivity:
```{r echo=FALSE}
tbd21 <- tboot_f2 - tboot_f1
tbd32 <- tboot_f3 - tboot_f2
tbd43 <- tboot_f4 - tboot_f3
tbd31 <- tboot_f3 - tboot_f1
tbd42 <- tboot_f4 - tboot_f2
tbd41 <- tboot_f4 - tboot_f1

par(mfrow = c(3, 2))
hist(tbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(tbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(tbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(tbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(tbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(tbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

Mean Degree:
```{r echo=FALSE}
mdbd21 <- mdboot_f2 - mdboot_f1
mdbd32 <- mdboot_f3 - mdboot_f2
mdbd43 <- mdboot_f4 - mdboot_f3
mdbd31 <- mdboot_f3 - mdboot_f1
mdbd42 <- mdboot_f4 - mdboot_f2
mdbd41 <- mdboot_f4 - mdboot_f1

par(mfrow = c(3, 2))
hist(mdbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(mdbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(mdbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(mdbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(mdbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(mdbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(mdbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

Edge Density:
```{r echo=FALSE}
dbd21 <- dboot_f2 - dboot_f1
dbd32 <- dboot_f3 - dboot_f2
dbd43 <- dboot_f4 - dboot_f3
dbd31 <- dboot_f3 - dboot_f1
dbd42 <- dboot_f4 - dboot_f2
dbd41 <- dboot_f4 - dboot_f1

par(mfrow = c(3, 2))
hist(dbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(dbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(dbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(dbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(dbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(dbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(dbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
kbd21 <- kboot_f2 - kboot_f1
kbd32 <- kboot_f3 - kboot_f2
kbd43 <- kboot_f4 - kboot_f3
kbd31 <- kboot_f3 - kboot_f1
kbd42 <- kboot_f4 - kboot_f2
kbd41 <- kboot_f4 - kboot_f1

par(mfrow = c(3, 2))
hist(kbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(kbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(kbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(kbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(kbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(kbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(kbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

## Jackknife distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

Transitivity:
```{r echo=FALSE}
tjd21 <- tjack_f2 - tjack_f1
tjd32 <- tjack_f3 - tjack_f2
tjd43 <- tjack_f4 - tjack_f3
tjd31 <- tjack_f3 - tjack_f1
tjd42 <- tjack_f4 - tjack_f2
tjd41 <- tjack_f4 - tjack_f1

par(mfrow = c(3, 2))
hist(tjd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tjd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(tjd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(tjd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(tjd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(tjd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(tjd41, c(0.025, 0.975)), col = "red", lwd=2)
```

Mean Degree:
```{r echo=FALSE}
mdjd21 <- mdjack_f2 - mdjack_f1
mdjd32 <- mdjack_f3 - mdjack_f2
mdjd43 <- mdjack_f4 - mdjack_f3
mdjd31 <- mdjack_f3 - mdjack_f1
mdjd42 <- mdjack_f4 - mdjack_f2
mdjd41 <- mdjack_f4 - mdjack_f1

par(mfrow = c(3, 2))
hist(mdjd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(mdjd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(mdjd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(mdjd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(mdjd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(mdjd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(mdjd41, c(0.025, 0.975)), col = "red", lwd=2)
```

Edge Density:
```{r echo=FALSE}
djd21 <- djack_f2 - djack_f1
djd32 <- djack_f3 - djack_f2
djd43 <- djack_f4 - djack_f3
djd31 <- djack_f3 - djack_f1
djd42 <- djack_f4 - djack_f2
djd41 <- djack_f4 - djack_f1

par(mfrow = c(3, 2))
hist(djd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(djd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(djd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(djd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(djd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(djd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(djd41, c(0.025, 0.975)), col = "red", lwd=2)
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
kjd21 <- kjack_f2 - kjack_f1
kjd32 <- kjack_f3 - kjack_f2
kjd43 <- kjack_f4 - kjack_f3
kjd31 <- kjack_f3 - kjack_f1
kjd42 <- kjack_f4 - kjack_f2
kjd41 <- kjack_f4 - kjack_f1

par(mfrow = c(3, 2))
hist(kjd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(kjd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(kjd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(kjd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(kjd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(kjd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(kjd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### If we assume that the distributions are normal, do we see significance in the same places?
**Bootstrap distributions:**

Transitivity:
```{r echo=FALSE}
t.test(tboot_f2, tboot_f1, paired = TRUE, alternative = "two.sided")
t.test(tboot_f3, tboot_f2, paired = TRUE, alternative = "two.sided")
t.test(tboot_f4, tboot_f3, paired = TRUE, alternative = "two.sided")
t.test(tboot_f3, tboot_f1, paired = TRUE, alternative = "two.sided")
t.test(tboot_f4, tboot_f2, paired = TRUE, alternative = "two.sided")
t.test(tboot_f4, tboot_f1, paired = TRUE, alternative = "two.sided")
```

Mean Degree:
```{r echo=FALSE}
t.test(mdboot_f2, mdboot_f1, paired = TRUE, alternative = "two.sided")
t.test(mdboot_f3, mdboot_f2, paired = TRUE, alternative = "two.sided")
t.test(mdboot_f4, mdboot_f3, paired = TRUE, alternative = "two.sided")
t.test(mdboot_f3, mdboot_f1, paired = TRUE, alternative = "two.sided")
t.test(mdboot_f4, mdboot_f2, paired = TRUE, alternative = "two.sided")
t.test(mdboot_f4, mdboot_f1, paired = TRUE, alternative = "two.sided")
```

Edge Density:
```{r echo=FALSE}
t.test(dboot_f2, dboot_f1, paired = TRUE, alternative = "two.sided")
t.test(dboot_f3, dboot_f2, paired = TRUE, alternative = "two.sided")
t.test(dboot_f4, dboot_f3, paired = TRUE, alternative = "two.sided")
t.test(dboot_f3, dboot_f1, paired = TRUE, alternative = "two.sided")
t.test(dboot_f4, dboot_f2, paired = TRUE, alternative = "two.sided")
t.test(dboot_f4, dboot_f1, paired = TRUE, alternative = "two.sided")
```

Number of nodes in k-cores where k > 1:

*Data are essentially constant.*

**Jackknife distributions:**

Transitivity:
```{r echo=FALSE}
t.test(tjack_f2, tjack_f1, paired = TRUE, alternative = "two.sided")
t.test(tjack_f3, tjack_f2, paired = TRUE, alternative = "two.sided")
t.test(tjack_f4, tjack_f3, paired = TRUE, alternative = "two.sided")
t.test(tjack_f3, tjack_f1, paired = TRUE, alternative = "two.sided")
t.test(tjack_f4, tjack_f2, paired = TRUE, alternative = "two.sided")
t.test(tjack_f4, tjack_f1, paired = TRUE, alternative = "two.sided")
```

Mean Degree:
```{r echo=FALSE}
t.test(mdjack_f2, mdjack_f1, paired = TRUE, alternative = "two.sided")
t.test(mdjack_f3, mdjack_f2, paired = TRUE, alternative = "two.sided")
t.test(mdjack_f4, mdjack_f3, paired = TRUE, alternative = "two.sided")
t.test(mdjack_f3, mdjack_f1, paired = TRUE, alternative = "two.sided")
t.test(mdjack_f4, mdjack_f2, paired = TRUE, alternative = "two.sided")
t.test(mdjack_f4, mdjack_f1, paired = TRUE, alternative = "two.sided")
```

Edge Density:
```{r echo=FALSE}
t.test(djack_f2, djack_f1, paired = TRUE, alternative = "two.sided")
t.test(djack_f3, djack_f2, paired = TRUE, alternative = "two.sided")
t.test(djack_f4, djack_f3, paired = TRUE, alternative = "two.sided")
t.test(djack_f3, djack_f1, paired = TRUE, alternative = "two.sided")
t.test(djack_f4, djack_f2, paired = TRUE, alternative = "two.sided")
t.test(djack_f4, djack_f1, paired = TRUE, alternative = "two.sided")
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
t.test(kjack_f2, kjack_f1, paired = TRUE, alternative = "two.sided")
t.test(kjack_f3, kjack_f2, paired = TRUE, alternative = "two.sided")
t.test(kjack_f4, kjack_f3, paired = TRUE, alternative = "two.sided")
t.test(kjack_f3, kjack_f1, paired = TRUE, alternative = "two.sided")
t.test(kjack_f4, kjack_f2, paired = TRUE, alternative = "two.sided")
t.test(kjack_f4, kjack_f1, paired = TRUE, alternative = "two.sided")
```

# Tortoise Interactions
Data source: 

- **The Network Data Repository with Interactive Graph Analytics and Visualization**
- Ryan A. Rossi and Nesreen K. Ahmed
- *AAAI*
- [http://networkrepository.com/](http://networkrepository.com/)
- 2015\

## Original Tortoise Networks
**Note: I omitted the network data from the year 1996 because there were only 7 data points, and because I reduced each network to only contain the intersection of nodes, using 1996 would have resulted in too few tortoises.**

```{r echo=FALSE}
plot(tg97, layout=layout_in_circle(tg97), main = "Tortoise interactions in 1997", 
     vertex.label.cex=0.35, vertex.size=5)
```
Transitivity: `r transitivity(tg97)`, Mean Degree: `r mean(degree(tg97))`, Edge Density: `r edge_density(tg97)`, Number of nodes in a k-core where k > 1: `r sum(coreness(tg97) > 1)`\

```{r echo=FALSE}
plot(tg98, layout=layout_in_circle(tg98), main = "Tortoise interactions in 1998", 
     vertex.label.cex=0.35, vertex.size=5)
```
Transitivity: `r transitivity(tg98)`, Mean Degree: `r mean(degree(tg98))`, Edge Density: `r edge_density(tg98)`, Number of nodes in a k-core where k > 1: `r sum(coreness(tg98) > 1)`\

```{r echo=FALSE}
plot(tg99, layout=layout_in_circle(tg99), main = "Tortoise interactions in 1999", 
     vertex.label.cex=0.35, vertex.size=5)
```
Transitivity: `r transitivity(tg99)`, Mean Degree: `r mean(degree(tg99))`, Edge Density: `r edge_density(tg99)`, Number of nodes in a k-core where k > 1: `r sum(coreness(tg99) > 1)`\

## Vertex Bootstrapped Distributions of Network Statistics
Transitivity:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(tboot_tg97, main = "1997",
    xlab = "Transitivity", col = "turquoise")
hist(tboot_tg98, main = "1998",
    xlab = "Transitivity", col = "lavender")
hist(tboot_tg99, main = "1999",
    xlab = "Transitivity", col = "lightblue")
```

Mean Degree:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(mdboot_tg97, main = "1997",
    xlab = "Mean Degree", col = "turquoise")
hist(mdboot_tg98, main = "1998",
    xlab = "Mean Degree", col = "lavender")
hist(mdboot_tg99, main = "1999",
    xlab = "Mean Degree", col = "lightblue")
```

Edge Density:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(dboot_tg97, main = "1997",
    xlab = "Density", col = "turquoise")
hist(dboot_tg98, main = "1998",
    xlab = "Density", col = "lavender")
hist(dboot_tg99, main = "1999",
    xlab = "Density", col = "lightblue")
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(kboot_tg97, main = "1997",
    xlab = "Quantity", col = "turquoise")
hist(kboot_tg98, main = "1998",
    xlab = "Quantity", col = "lavender")
hist(kboot_tg99, main = "1999",
    xlab = "Quantity", col = "lightblue")
```

## Vertex Jackknife Distributions of Network Statistics
Transitivity:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(tjack_tg97, main = "1997",
    xlab = "Transitivity", col = "turquoise")
hist(tjack_tg98, main = "1998",
    xlab = "Transitivity", col = "lavender")
hist(tjack_tg99, main = "1999",
    xlab = "Transitivity", col = "lightblue")
```

Mean Degree:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(mdjack_tg97, main = "1997",
    xlab = "Mean Degree", col = "turquoise")
hist(mdjack_tg98, main = "1998",
    xlab = "Mean Degree", col = "lavender")
hist(mdjack_tg99, main = "1999",
    xlab = "Mean Degree", col = "lightblue")
```

Edge Density:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(djack_tg97, main = "1997",
    xlab = "Density", col = "turquoise")
hist(djack_tg98, main = "1998",
    xlab = "Density", col = "lavender")
hist(djack_tg99, main = "1999",
    xlab = "Density", col = "lightblue")
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
par(mfrow = c(2, 2))
hist(kjack_tg97, main = "1997",
    xlab = "Quantity", col = "turquoise")
hist(kjack_tg98, main = "1998",
    xlab = "Quantity", col = "lavender")
hist(kjack_tg99, main = "1999",
    xlab = "Quantity", col = "lightblue")
```

## Bootstrap distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

Transitivity:
```{r echo=FALSE}
ttbd1 <- tboot_tg98 - tboot_tg97
ttbd2 <- tboot_tg99 - tboot_tg98
ttbd3 <- tboot_tg99 - tboot_tg97

par(mfrow = c(2, 2))
hist(ttbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(ttbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(ttbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(ttbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

Mean Degree:
```{r echo=FALSE}
tmdbd1 <- mdboot_tg98 - mdboot_tg97
tmdbd2 <- mdboot_tg99 - mdboot_tg98
tmdbd3 <- mdboot_tg99 - mdboot_tg97

par(mfrow = c(2, 2))
hist(tmdbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tmdbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tmdbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tmdbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

Edge Density:
```{r echo=FALSE}
tdbd1 <- dboot_tg98 - dboot_tg97
tdbd2 <- dboot_tg99 - dboot_tg98
tdbd3 <- dboot_tg99 - dboot_tg97

par(mfrow = c(2, 2))
hist(tdbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tdbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tdbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tdbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
tkbd1 <- kboot_tg98 - kboot_tg97
tkbd2 <- kboot_tg99 - kboot_tg98
tkbd3 <- kboot_tg99 - kboot_tg97

par(mfrow = c(2, 2))
hist(tkbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tkbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tkbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tkbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

## Jackknife distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

Transitivity:
```{r echo=FALSE}
ttjd1 <- tjack_tg98 - tjack_tg97
ttjd2 <- tjack_tg99 - tjack_tg98
ttjd3 <- tjack_tg99 - tjack_tg97

par(mfrow = c(2, 2))
hist(ttjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(ttjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(ttjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(ttjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

Mean Degree:
```{r echo=FALSE}
tmdjd1 <- mdjack_tg98 - mdjack_tg97
tmdjd2 <- mdjack_tg99 - mdjack_tg98
tmdjd3 <- mdjack_tg99 - mdjack_tg97

par(mfrow = c(2, 2))
hist(tmdjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tmdjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tmdjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tmdjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

Edge Density:
```{r echo=FALSE}
tdjd1 <- djack_tg98 - djack_tg97
tdjd2 <- djack_tg99 - djack_tg98
tdjd3 <- djack_tg99 - djack_tg97

par(mfrow = c(2, 2))
hist(tdjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tdjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tdjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tdjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
tkjd1 <- kjack_tg98 - kjack_tg97
tkjd2 <- kjack_tg99 - kjack_tg98
tkjd3 <- kjack_tg99 - kjack_tg97

par(mfrow = c(2, 2))
hist(tkjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tkjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tkjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tkjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### If we assume that the distributions are normal, do we see significance in the same places?
**Bootstrap distributions:**

Transitivity:
```{r echo=FALSE}
t.test(tboot_tg98, tboot_tg97, paired = TRUE, alternative = "two.sided")
t.test(tboot_tg99, tboot_tg98, paired = TRUE, alternative = "two.sided")
t.test(tboot_tg99, tboot_tg97, paired = TRUE, alternative = "two.sided")
```

Mean Degree:
```{r echo=FALSE}
t.test(mdboot_tg98, mdboot_tg97, paired = TRUE, alternative = "two.sided")
t.test(mdboot_tg99, mdboot_tg98, paired = TRUE, alternative = "two.sided")
t.test(mdboot_tg99, mdboot_tg97, paired = TRUE, alternative = "two.sided")
```

Edge Density:
```{r echo=FALSE}
t.test(dboot_tg98, dboot_tg97, paired = TRUE, alternative = "two.sided")
t.test(dboot_tg99, dboot_tg98, paired = TRUE, alternative = "two.sided")
t.test(dboot_tg99, dboot_tg97, paired = TRUE, alternative = "two.sided")
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
t.test(kboot_tg98, kboot_tg97, paired = TRUE, alternative = "two.sided")
t.test(kboot_tg99, kboot_tg98, paired = TRUE, alternative = "two.sided")
t.test(kboot_tg99, kboot_tg97, paired = TRUE, alternative = "two.sided")
```

**Jackknife distributions:**

Transitivity:
```{r echo=FALSE}
t.test(tjack_tg98, tjack_tg97, paired = TRUE, alternative = "two.sided")
t.test(tjack_tg99, tjack_tg98, paired = TRUE, alternative = "two.sided")
t.test(tjack_tg99, tjack_tg97, paired = TRUE, alternative = "two.sided")
```

Mean Degree:
```{r echo=FALSE}
t.test(mdjack_tg98, mdjack_tg97, paired = TRUE, alternative = "two.sided")
t.test(mdjack_tg99, mdjack_tg98, paired = TRUE, alternative = "two.sided")
t.test(mdjack_tg99, mdjack_tg97, paired = TRUE, alternative = "two.sided")
```

Edge Density:
```{r echo=FALSE}
t.test(djack_tg98, djack_tg97, paired = TRUE, alternative = "two.sided")
t.test(djack_tg99, djack_tg98, paired = TRUE, alternative = "two.sided")
t.test(djack_tg99, djack_tg97, paired = TRUE, alternative = "two.sided")
```

Number of nodes in k-cores where k > 1:
```{r echo=FALSE}
t.test(kjack_tg98, kjack_tg97, paired = TRUE, alternative = "two.sided")
t.test(kjack_tg99, kjack_tg98, paired = TRUE, alternative = "two.sided")
t.test(kjack_tg99, kjack_tg97, paired = TRUE, alternative = "two.sided")
```

