---
title: "Visualizations of Network Statistics Over Time Using Vertex Bootstrap and Jackknife"
author: "Alan Sun"
date: "7/15/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
load("env.RData")
```

This document contains tables and visualizations regarding distributions of the differences in several network statistics over time. The distributions are obtained using the vertex bootstrap and jackknife procedures. Two different temporal networks are examined.

Source code (to generate distributions): [https://github.com/alansun25/network-analysis/blob/main/analysis/vert-jack-viz.R](https://github.com/alansun25/network-analysis/blob/main/analysis/vert-jack-viz.R)

# Friendship in a Dutch school class
Data source:

- **[RSiena](https://www.stats.ox.ac.uk/~snijders/siena/)**
- Andrea Knecht
- [https://www.stats.ox.ac.uk/~snijders/siena/tutorial2010_data.htm](https://www.stats.ox.ac.uk/~snijders/siena/tutorial2010_data.htm)
- 2008\

## Original Friendship Networks

```{r echo=FALSE, fig.align='center'}
plot(fg1, layout=layout_with_kk(fg1), main = "Friendships at time 1", vertex.label.cex=0.7, vertex.size=10)
```

Transitivity: `r transitivity(fg1)`, Mean Degree: `r mean(degree(fg1))`, Edge Density: `r edge_density(fg1)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg1) > 1)`\

```{r echo=FALSE, fig.align='center'}
plot(fg2, layout=layout_with_kk(fg1), main = "Friendships at time 2 (Three months after time 1)", vertex.label.cex=0.7, vertex.size=10)
```

Transitivity: `r transitivity(fg2)`, Mean Degree: `r mean(degree(fg2))`, Edge Density: `r edge_density(fg2)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg2) > 1)`\

```{r echo=FALSE, fig.align='center'}
plot(fg3, layout=layout_with_kk(fg1), main = "Friendships at time 3 (Three months after time 2)", vertex.label.cex=0.7,
     vertex.size=10)
```

Transitivity: `r transitivity(fg3)`, Mean Degree: `r mean(degree(fg3))`, Edge Density: `r edge_density(fg3)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg3) > 1)`\

```{r echo=FALSE, fig.align='center'}
plot(fg4, layout=layout_with_kk(fg1), main = "Friendships at time 4 (Three months after time 3)", vertex.label.cex=0.7,
     vertex.size=10)
```

Transitivity: `r transitivity(fg4)`, Mean Degree: `r mean(degree(fg4))`, Edge Density: `r edge_density(fg4)`, Number of nodes in a k-core where k > 1: `r sum(coreness(fg4) > 1)`\

## Vertex Bootstrapped Distributions of Network Statistics
### Transitivity:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(tboot_f1, main = "Time 1",
    xlab = "Transitivity", col = "turquoise")
hist(tboot_f2, main = "Time 2",
    xlab = "Transitivity", col = "lavender")
hist(tboot_f3, main = "Time 3",
    xlab = "Transitivity", col = "lightblue")
hist(tboot_f4, main = "Time 4",
    xlab = "Transitivity", col = "gold")
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(mboot_f1, main = "Time 1",
    xlab = "Mean Degree", col = "turquoise")
hist(mboot_f2, main = "Time 2",
    xlab = "Mean Degree", col = "lavender")
hist(mboot_f3, main = "Time 3",
    xlab = "Mean Degree", col = "lightblue")
hist(mboot_f4, main = "Time 4",
    xlab = "Mean Degree", col = "gold")
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(dboot_f1, main = "Time 1",
    xlab = "Density", col = "turquoise")
hist(dboot_f2, main = "Time 2",
    xlab = "Density", col = "lavender")
hist(dboot_f3, main = "Time 3",
    xlab = "Density", col = "lightblue")
hist(dboot_f4, main = "Time 4",
    xlab = "Density", col = "gold")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(kboot_f1, main = "Time 1",
    xlab = "Quantity", col = "turquoise")
hist(kboot_f2, main = "Time 2",
    xlab = "Quantity", col = "lavender")
hist(kboot_f3, main = "Time 3",
    xlab = "Quantity", col = "lightblue")
hist(kboot_f4, main = "Time 4",
    xlab = "Quantity", col = "gold")
```

## Vertex Jackknife Distributions of Network Statistics
### Transitivity:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(tjack_f1, main = "Time 1",
    xlab = "Transitivity", col = "turquoise")
hist(tjack_f2, main = "Time 2",
    xlab = "Transitivity", col = "lavender")
hist(tjack_f3, main = "Time 3",
    xlab = "Transitivity", col = "lightblue")
hist(tjack_f4, main = "Time 4",
    xlab = "Transitivity", col = "gold")
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(mjack_f1, main = "Time 1",
    xlab = "Mean Degree", col = "turquoise")
hist(mjack_f2, main = "Time 2",
    xlab = "Mean Degree", col = "lavender")
hist(mjack_f3, main = "Time 3",
    xlab = "Mean Degree", col = "lightblue")
hist(mjack_f4, main = "Time 4",
    xlab = "Mean Degree", col = "gold")
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(djack_f1, main = "Time 1",
    xlab = "Density", col = "turquoise")
hist(djack_f2, main = "Time 2",
    xlab = "Density", col = "lavender")
hist(djack_f3, main = "Time 3",
    xlab = "Density", col = "lightblue")
hist(djack_f4, main = "Time 4",
    xlab = "Density", col = "gold")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(kjack_f1, main = "Time 1",
    xlab = "Quantity", col = "turquoise")
hist(kjack_f2, main = "Time 2",
    xlab = "Quantity", col = "lavender")
hist(kjack_f3, main = "Time 3",
    xlab = "Quantity", col = "lightblue")
hist(kjack_f4, main = "Time 4",
    xlab = "Quantity", col = "gold")
```

## Bootstrap distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

### Transitivity:

```{r echo=FALSE, fig.align='center'}
tbd21 <- tboot_f2 - tboot_f1
tbd32 <- tboot_f3 - tboot_f2
tbd43 <- tboot_f4 - tboot_f3
tbd31 <- tboot_f3 - tboot_f1
tbd42 <- tboot_f4 - tboot_f2
tbd41 <- tboot_f4 - tboot_f1

par(mfrow = c(3, 2))
hist(tbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(tbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(tbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(tbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(tbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(tbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(tbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
mdbd21 <- mboot_f2 - mboot_f1
mdbd32 <- mboot_f3 - mboot_f2
mdbd43 <- mboot_f4 - mboot_f3
mdbd31 <- mboot_f3 - mboot_f1
mdbd42 <- mboot_f4 - mboot_f2
mdbd41 <- mboot_f4 - mboot_f1

par(mfrow = c(3, 2))
hist(mdbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(mdbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(mdbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(mdbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(mdbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(mdbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(mdbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
dbd21 <- dboot_f2 - dboot_f1
dbd32 <- dboot_f3 - dboot_f2
dbd43 <- dboot_f4 - dboot_f3
dbd31 <- dboot_f3 - dboot_f1
dbd42 <- dboot_f4 - dboot_f2
dbd41 <- dboot_f4 - dboot_f1

par(mfrow = c(3, 2))
hist(dbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(dbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(dbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(dbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(dbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(dbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(dbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(dbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
kbd21 <- kboot_f2 - kboot_f1
kbd32 <- kboot_f3 - kboot_f2
kbd43 <- kboot_f4 - kboot_f3
kbd31 <- kboot_f3 - kboot_f1
kbd42 <- kboot_f4 - kboot_f2
kbd41 <- kboot_f4 - kboot_f1

par(mfrow = c(3, 2))
hist(kbd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(kbd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(kbd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(kbd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(kbd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(kbd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(kbd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(kbd41, c(0.025, 0.975)), col = "red", lwd=2)
```

## Jackknife distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

### Transitivity:

```{r echo=FALSE, fig.align='center'}
tjd21 <- tjack_f2 - tjack_f1
tjd32 <- tjack_f3 - tjack_f2
tjd43 <- tjack_f4 - tjack_f3
tjd31 <- tjack_f3 - tjack_f1
tjd42 <- tjack_f4 - tjack_f2
tjd41 <- tjack_f4 - tjack_f1

par(mfrow = c(3, 2))
hist(tjd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tjd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(tjd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(tjd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(tjd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(tjd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(tjd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(tjd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
mdjd21 <- mjack_f2 - mjack_f1
mdjd32 <- mjack_f3 - mjack_f2
mdjd43 <- mjack_f4 - mjack_f3
mdjd31 <- mjack_f3 - mjack_f1
mdjd42 <- mjack_f4 - mjack_f2
mdjd41 <- mjack_f4 - mjack_f1

par(mfrow = c(3, 2))
hist(mdjd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(mdjd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(mdjd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(mdjd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(mdjd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(mdjd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(mdjd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(mdjd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
djd21 <- djack_f2 - djack_f1
djd32 <- djack_f3 - djack_f2
djd43 <- djack_f4 - djack_f3
djd31 <- djack_f3 - djack_f1
djd42 <- djack_f4 - djack_f2
djd41 <- djack_f4 - djack_f1

par(mfrow = c(3, 2))
hist(djd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(djd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(djd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(djd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(djd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(djd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(djd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(djd41, c(0.025, 0.975)), col = "red", lwd=2)
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
kjd21 <- kjack_f2 - kjack_f1
kjd32 <- kjack_f3 - kjack_f2
kjd43 <- kjack_f4 - kjack_f3
kjd31 <- kjack_f3 - kjack_f1
kjd42 <- kjack_f4 - kjack_f2
kjd41 <- kjack_f4 - kjack_f1

par(mfrow = c(3, 2))
hist(kjd21, main = "Time 2 - Time 1", xlab = "Difference", col = "aquamarine")
abline(v = quantile(kjd21, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd32, main = "Time 3 - Time 2", xlab = "Difference", col = "plum2")
abline(v = quantile(kjd32, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd43, main = "Time 4 - Time 3", xlab = "Difference", col = "khaki1")
abline(v = quantile(kjd43, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd31, main = "Time 3 - Time 1", xlab = "Difference", col = "olivedrab2")
abline(v = quantile(kjd31, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd42, main = "Time 4 - Time 2", xlab = "Difference", col = "purple1")
abline(v = quantile(kjd42, c(0.025, 0.975)), col = "red", lwd=2)
hist(kjd41, main = "Time 4 - Time 1", xlab = "Difference", col = "slateblue")
abline(v = quantile(kjd41, c(0.025, 0.975)), col = "red", lwd=2)
```

## If we assume that the distributions are normal, do we see significance in the same places?
**Bootstrap distributions:**

### Transitivity:

```{r echo=FALSE, fig.align='center'}
t.test(tboot_f2, tboot_f1, paired = TRUE, alternative = "two.sided")
t.test(tboot_f3, tboot_f2, paired = TRUE, alternative = "two.sided")
t.test(tboot_f4, tboot_f3, paired = TRUE, alternative = "two.sided")
t.test(tboot_f3, tboot_f1, paired = TRUE, alternative = "two.sided")
t.test(tboot_f4, tboot_f2, paired = TRUE, alternative = "two.sided")
t.test(tboot_f4, tboot_f1, paired = TRUE, alternative = "two.sided")
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
t.test(mboot_f2, mboot_f1, paired = TRUE, alternative = "two.sided")
t.test(mboot_f3, mboot_f2, paired = TRUE, alternative = "two.sided")
t.test(mboot_f4, mboot_f3, paired = TRUE, alternative = "two.sided")
t.test(mboot_f3, mboot_f1, paired = TRUE, alternative = "two.sided")
t.test(mboot_f4, mboot_f2, paired = TRUE, alternative = "two.sided")
t.test(mboot_f4, mboot_f1, paired = TRUE, alternative = "two.sided")
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
t.test(dboot_f2, dboot_f1, paired = TRUE, alternative = "two.sided")
t.test(dboot_f3, dboot_f2, paired = TRUE, alternative = "two.sided")
t.test(dboot_f4, dboot_f3, paired = TRUE, alternative = "two.sided")
t.test(dboot_f3, dboot_f1, paired = TRUE, alternative = "two.sided")
t.test(dboot_f4, dboot_f2, paired = TRUE, alternative = "two.sided")
t.test(dboot_f4, dboot_f1, paired = TRUE, alternative = "two.sided")
```

### Number of nodes in k-cores where k > 1:

*Data are essentially constant.*

**Jackknife distributions:**

### Transitivity:

```{r echo=FALSE}
t.test(tjack_f2, tjack_f1, paired = TRUE, alternative = "two.sided")
t.test(tjack_f3, tjack_f2, paired = TRUE, alternative = "two.sided")
t.test(tjack_f4, tjack_f3, paired = TRUE, alternative = "two.sided")
t.test(tjack_f3, tjack_f1, paired = TRUE, alternative = "two.sided")
t.test(tjack_f4, tjack_f2, paired = TRUE, alternative = "two.sided")
t.test(tjack_f4, tjack_f1, paired = TRUE, alternative = "two.sided")
```

### Mean Degree:

```{r echo=FALSE}
t.test(mjack_f2, mjack_f1, paired = TRUE, alternative = "two.sided")
t.test(mjack_f3, mjack_f2, paired = TRUE, alternative = "two.sided")
t.test(mjack_f4, mjack_f3, paired = TRUE, alternative = "two.sided")
t.test(mjack_f3, mjack_f1, paired = TRUE, alternative = "two.sided")
t.test(mjack_f4, mjack_f2, paired = TRUE, alternative = "two.sided")
t.test(mjack_f4, mjack_f1, paired = TRUE, alternative = "two.sided")
```

### Edge Density:

```{r echo=FALSE}
t.test(djack_f2, djack_f1, paired = TRUE, alternative = "two.sided")
t.test(djack_f3, djack_f2, paired = TRUE, alternative = "two.sided")
t.test(djack_f4, djack_f3, paired = TRUE, alternative = "two.sided")
t.test(djack_f3, djack_f1, paired = TRUE, alternative = "two.sided")
t.test(djack_f4, djack_f2, paired = TRUE, alternative = "two.sided")
t.test(djack_f4, djack_f1, paired = TRUE, alternative = "two.sided")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE}
t.test(kjack_f2, kjack_f1, paired = TRUE, alternative = "two.sided")
t.test(kjack_f3, kjack_f2, paired = TRUE, alternative = "two.sided")
t.test(kjack_f4, kjack_f3, paired = TRUE, alternative = "two.sided")
t.test(kjack_f3, kjack_f1, paired = TRUE, alternative = "two.sided")
t.test(kjack_f4, kjack_f2, paired = TRUE, alternative = "two.sided")
t.test(kjack_f4, kjack_f1, paired = TRUE, alternative = "two.sided")
```

# Tortoise Interactions
Data source: 

- **The Network Data Repository with Interactive Graph Analytics and Visualization**
- Ryan A. Rossi and Nesreen K. Ahmed
- *AAAI*
- [http://networkrepository.com/](http://networkrepository.com/)
- 2015\

## Original Tortoise Networks
**Note: I omitted the network data from the year 1996 because there were only 7 data points, and because I reduced each network to only contain the intersection of nodes, using 1996 would have resulted in too few tortoises.**

```{r echo=FALSE, fig.align='center'}
plot(tg97, layout=layout_with_fr(tg97), main = "Tortoise interactions in 1997", 
     vertex.label.cex=0.35, vertex.size=5)
```

Transitivity: `r transitivity(tg97)`, Mean Degree: `r mean(degree(tg97))`, Edge Density: `r edge_density(tg97)`, Number of nodes in a k-core where k > 1: `r sum(coreness(tg97) > 1)`\

```{r echo=FALSE, fig.align='center'}
plot(tg98, layout=layout_with_fr(tg97), main = "Tortoise interactions in 1998", 
     vertex.label.cex=0.35, vertex.size=5)
```

Transitivity: `r transitivity(tg98)`, Mean Degree: `r mean(degree(tg98))`, Edge Density: `r edge_density(tg98)`, Number of nodes in a k-core where k > 1: `r sum(coreness(tg98) > 1)`\

```{r echo=FALSE, fig.align='center'}
plot(tg99, layout=layout_with_fr(tg97), main = "Tortoise interactions in 1999", 
     vertex.label.cex=0.35, vertex.size=5)
```

Transitivity: `r transitivity(tg99)`, Mean Degree: `r mean(degree(tg99))`, Edge Density: `r edge_density(tg99)`, Number of nodes in a k-core where k > 1: `r sum(coreness(tg99) > 1)`\

## Vertex Bootstrapped Distributions of Network Statistics
### Transitivity:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(tboot_t97, main = "1997",
    xlab = "Transitivity", col = "turquoise")
hist(tboot_t98, main = "1998",
    xlab = "Transitivity", col = "lavender")
hist(tboot_t99, main = "1999",
    xlab = "Transitivity", col = "lightblue")
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(mboot_t97, main = "1997",
    xlab = "Mean Degree", col = "turquoise")
hist(mboot_t98, main = "1998",
    xlab = "Mean Degree", col = "lavender")
hist(mboot_t99, main = "1999",
    xlab = "Mean Degree", col = "lightblue")
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(dboot_t97, main = "1997",
    xlab = "Density", col = "turquoise")
hist(dboot_t98, main = "1998",
    xlab = "Density", col = "lavender")
hist(dboot_t99, main = "1999",
    xlab = "Density", col = "lightblue")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(kboot_t97, main = "1997",
    xlab = "Quantity", col = "turquoise")
hist(kboot_t98, main = "1998",
    xlab = "Quantity", col = "lavender")
hist(kboot_t99, main = "1999",
    xlab = "Quantity", col = "lightblue")
```

## Vertex Jackknife Distributions of Network Statistics
### Transitivity:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(tjack_t97, main = "1997",
    xlab = "Transitivity", col = "turquoise")
hist(tjack_t98, main = "1998",
    xlab = "Transitivity", col = "lavender")
hist(tjack_t99, main = "1999",
    xlab = "Transitivity", col = "lightblue")
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(mjack_t97, main = "1997",
    xlab = "Mean Degree", col = "turquoise")
hist(mjack_t98, main = "1998",
    xlab = "Mean Degree", col = "lavender")
hist(mjack_t99, main = "1999",
    xlab = "Mean Degree", col = "lightblue")
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(djack_t97, main = "1997",
    xlab = "Density", col = "turquoise")
hist(djack_t98, main = "1998",
    xlab = "Density", col = "lavender")
hist(djack_t99, main = "1999",
    xlab = "Density", col = "lightblue")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
par(mfrow = c(2, 2))
hist(kjack_t97, main = "1997",
    xlab = "Quantity", col = "turquoise")
hist(kjack_t98, main = "1998",
    xlab = "Quantity", col = "lavender")
hist(kjack_t99, main = "1999",
    xlab = "Quantity", col = "lightblue")
```

## Bootstrap distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

### Transitivity:

```{r echo=FALSE, fig.align='center'}
ttbd1 <- tboot_t98 - tboot_t97
ttbd2 <- tboot_t99 - tboot_t98
ttbd3 <- tboot_t99 - tboot_t97

par(mfrow = c(2, 2))
hist(ttbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(ttbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(ttbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(ttbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
tmdbd1 <- mboot_t98 - mboot_t97
tmdbd2 <- mboot_t99 - mboot_t98
tmdbd3 <- mboot_t99 - mboot_t97

par(mfrow = c(2, 2))
hist(tmdbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tmdbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tmdbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tmdbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
tdbd1 <- dboot_t98 - dboot_t97
tdbd2 <- dboot_t99 - dboot_t98
tdbd3 <- dboot_t99 - dboot_t97

par(mfrow = c(2, 2))
hist(tdbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tdbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tdbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tdbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
tkbd1 <- kboot_t98 - kboot_t97
tkbd2 <- kboot_t99 - kboot_t98
tkbd3 <- kboot_t99 - kboot_t97

par(mfrow = c(2, 2))
hist(tkbd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tkbd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkbd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tkbd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkbd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tkbd3, c(0.025, 0.975)), col = "red", lwd=2)
```

## Jackknife distributions of the differences in network statistics between time points

**The vertical red lines indicate the middle 95% of the distributions.**

### Transitivity:

```{r echo=FALSE, fig.align='center'}
ttjd1 <- tjack_t98 - tjack_t97
ttjd2 <- tjack_t99 - tjack_t98
ttjd3 <- tjack_t99 - tjack_t97

par(mfrow = c(2, 2))
hist(ttjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(ttjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(ttjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(ttjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(ttjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### Mean Degree:

```{r echo=FALSE, fig.align='center'}
tmdjd1 <- mjack_t98 - mjack_t97
tmdjd2 <- mjack_t99 - mjack_t98
tmdjd3 <- mjack_t99 - mjack_t97

par(mfrow = c(2, 2))
hist(tmdjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tmdjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tmdjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tmdjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tmdjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### Edge Density:

```{r echo=FALSE, fig.align='center'}
tdjd1 <- djack_t98 - djack_t97
tdjd2 <- djack_t99 - djack_t98
tdjd3 <- djack_t99 - djack_t97

par(mfrow = c(2, 2))
hist(tdjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tdjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tdjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tdjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tdjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE, fig.align='center'}
tkjd1 <- kjack_t98 - kjack_t97
tkjd2 <- kjack_t99 - kjack_t98
tkjd3 <- kjack_t99 - kjack_t97

par(mfrow = c(2, 2))
hist(tkjd1, main = "1998 - 1997", xlab = "Difference", col = "aquamarine")
abline(v = quantile(tkjd1, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkjd2, main = "1999 - 1998", xlab = "Difference", col = "plum2")
abline(v = quantile(tkjd2, c(0.025, 0.975)), col = "red", lwd=2)
hist(tkjd3, main = "1999 - 1997", xlab = "Difference", col = "khaki1")
abline(v = quantile(tkjd3, c(0.025, 0.975)), col = "red", lwd=2)
```

## If we assume that the distributions are normal, do we see significance in the same places?
**Bootstrap distributions:**

### Transitivity:

```{r echo=FALSE}
t.test(tboot_t98, tboot_t97, paired = TRUE, alternative = "two.sided")
t.test(tboot_t99, tboot_t98, paired = TRUE, alternative = "two.sided")
t.test(tboot_t99, tboot_t97, paired = TRUE, alternative = "two.sided")
```

### Mean Degree:

```{r echo=FALSE}
t.test(mboot_t98, mboot_t97, paired = TRUE, alternative = "two.sided")
t.test(mboot_t99, mboot_t98, paired = TRUE, alternative = "two.sided")
t.test(mboot_t99, mboot_t97, paired = TRUE, alternative = "two.sided")
```

### Edge Density:

```{r echo=FALSE}
t.test(dboot_t98, dboot_t97, paired = TRUE, alternative = "two.sided")
t.test(dboot_t99, dboot_t98, paired = TRUE, alternative = "two.sided")
t.test(dboot_t99, dboot_t97, paired = TRUE, alternative = "two.sided")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE}
t.test(kboot_t98, kboot_t97, paired = TRUE, alternative = "two.sided")
t.test(kboot_t99, kboot_t98, paired = TRUE, alternative = "two.sided")
t.test(kboot_t99, kboot_t97, paired = TRUE, alternative = "two.sided")
```

**Jackknife distributions:**

### Transitivity:

```{r echo=FALSE}
t.test(tjack_t98, tjack_t97, paired = TRUE, alternative = "two.sided")
t.test(tjack_t99, tjack_t98, paired = TRUE, alternative = "two.sided")
t.test(tjack_t99, tjack_t97, paired = TRUE, alternative = "two.sided")
```

### Mean Degree:

```{r echo=FALSE}
t.test(mjack_t98, mjack_t97, paired = TRUE, alternative = "two.sided")
t.test(mjack_t99, mjack_t98, paired = TRUE, alternative = "two.sided")
t.test(mjack_t99, mjack_t97, paired = TRUE, alternative = "two.sided")
```

### Edge Density:

```{r echo=FALSE}
t.test(djack_t98, djack_t97, paired = TRUE, alternative = "two.sided")
t.test(djack_t99, djack_t98, paired = TRUE, alternative = "two.sided")
t.test(djack_t99, djack_t97, paired = TRUE, alternative = "two.sided")
```

### Number of nodes in k-cores where k > 1:

```{r echo=FALSE}
t.test(kjack_t98, kjack_t97, paired = TRUE, alternative = "two.sided")
t.test(kjack_t99, kjack_t98, paired = TRUE, alternative = "two.sided")
t.test(kjack_t99, kjack_t97, paired = TRUE, alternative = "two.sided")
```

